Language-Based Security for Low-Level MPC

### 2024-09-02 ppdp24/slides.tex
checkpoint

@@

  The probability distribution of a protocol $\prog$ (as a pmf) can be precisely computed
  by interpretation as a \cemph{constraint program}.
  \begin{itemize}
  \item Interpretation as a Datalog program-- set of Least Herbrand Models.
    \begin{itemize}
      \item Random tapes represented as fact base.
    \end{itemize}
  \item Interpretation as SMT constraints \footnote{Ozdemir, A., Kremer, G., Tinelli, C., Barrett, C. (2023). \emph{Satisfiability Modulo Finite Fields}. In: Enea, C., Lal, A. (eds) Computer Aided Verification. CAV 2023. }-- set of all models.
  \end{itemize}
  Set of models can be queried to enforce hyperproperties-- but poor scaling.

>>>>

\section{Overview}

\begin{frame}{Background}

  \cemph{Secure Multiparty Computation (MPC)} is a paradigm for
  \cemph{confidential computing}.
  \begin{itemize}
  \item Guarantees data privacy.
  \item Software-based protocols (vs., e.g., enclaves).
  \item No trusted 3rd party.
  \end{itemize}
  Many existing deployments: voting, auctions, satellite trajectories, COVID exposure notification, ...\footnote{https://mpc.cs.berkeley.edu}

  \medskip

  Various language frameworks, including MPyC, Fairplay, Viaduct.
\end{frame}

\begin{frame}{Contributions}

  Existing HLLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Low-level protocols possess distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques manual, error prone, complex security model.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item (Re)formulation of security mode as \cemph{hyperoperties} (e.g., noninterference).
  \item Automated proof techniques.
  \end{itemize}

@@

  The probability distribution of a protocol $\prog$ (as a pmf) can be precisely computed
  by interpretation as a \cemph{constraint program}.
  \begin{itemize}
  \item Interpretation as a Datalog program-- set of Least Herbrand Models.
    \begin{itemize}
      \item Random tapes represented as fact base.
    \end{itemize}
  \item Interpretation as SMT constraints\footnote{Ozdemir, A., Kremer, G., Tinelli, C., Barrett, C. (2023). \emph{Satisfiability Modulo Finite Fields}. In: Enea, C., Lal, A. (eds) Computer Aided Verification. CAV 2023. }-- set of all models.
  \end{itemize}
  Set of models can be queried to enforce hyperproperties-- but poor scaling.
